Causal Analysis Paper

### 2022-06-06 PaperAnalysis.Rmd
Text update - summary of the article; bibliography added

---
title: "Causal_Analysis_Paper"
author: "Helena Bakic, Anna-Lisa Wirth, Ángela Duarte Pardo"
date: "5/23/2022"
output: html_document
---

@@

@@

In "Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries," Latt, Milner and Kavanagh present the results of a study that aims to assess whether maternal mortality is affected by the flexibility of abortion laws.

##  The causal design of the original paper

@@

@@

## Original Paper
- Latt, S.M., Milner, A. & Kavanagh, A.(2019) Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries. BMC Women's Health 19, 1. https://doi.org/10.1186/s12905-018-0705-y

@@

>>>>

---
title: "Causal Analysis Paper"
author: "Helena Bakic, Anna-Lisa Wirth, Ángela Duarte Pardo"
date: "5/23/2022"
output: html_document
bibliography: references.bib
---

@@

## Introduction

Introduction on abortion laws and motivation

@@

In "Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries," @Latt_2019 present the results of a study that aims to assess whether maternal mortality is affected by the flexibility of abortion laws. Abortion law flexibility was measured as a sum of the number of reasons for which abortion is legally allowed (ranging from 0 to 7) and was included in models as both an ordinal variable and a binary variable (inflexible vs. flexible abortion laws). Abortion laws were considered inflexible if there were less than 3 legal grounds for abortion. Maternal mortality ratio (MMR) was measured as the number of maternal deaths per 100,000 live births. Authors used fixed effects linear regression models to estimate the relationship between abortion law flexibility and MMR, while controlling for GDP per capita and time in five-year intervals. Additional analysis included also female primary education completion as a control variable as it had over 50% of missing data; however, results did not change. Results indicated that maternal deaths reduce by 45 per 100,000 live births (95% CI: -64, -26) with flexible abortion laws. Authors conclude that abortion law reform in countries with inflexible abortion laws may reduce maternal mortality.

##  Methodology

### Causal design

@@

## Conclusion

@@

@@

###Text
